---
title: "Bellabeat"
author: "Nathasya Pramudita"
date: "2023-11-04"
output:
  github_document:
    toc: TRUE
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Bellabeat Case Study.
## Introduction

Bellabeat is company that created health device for all ages, specifying for women.
Their product is not only prioritized function but creating unique appearance too.
Bellabeat is the go-to wellness brand for women with an ecosystem of products and services focused on women health. They created various product such as:

1. Wellness tracker
2. Yoga mat with sustainable material
3. Menstrual cup
4. And all the accessories for their wellness tracker device

## Dataset for the analysis

To observe Bellabeat's user behavior while using one of their best product, Wellness tracker.
We collect dataset from `FitBit Fitness Tracker Data` Distribute via Amazon Mechanical Turk between 12-04-2016 to 12-05-2016.

The dataset consist of:

* activity dataframe : Consist of 15 columns and 940 rows. It's about their behavior pattern when using the wellness tracker device. The dataset is from 2016-04-12 until 2016-05-12, with 33 unique `id` users.

* caloriesHour : Consist of 3 columns and 22.099 rows. It's about how much the user burn their calories every hours each day.

* heartrate : Consist of 3 variables with 2.482.658 rows. This dataframe is collecting every 5 seconds of the heartrate of our user while using the wellness tracker device.

* hourlySteps : Consist of 3 variables with 22.099 rows. It's about each and every steps our user achived every hours.

* sleepday : Consist of 5 variables with 431 rows. They record how long the user stay in bed and their REM sleep quality.

* weightLogInfo : With 8 variables and 67 rows. This dataset is about 8 unique users identity of weight, BMI, and last log in and out of the platform.

# Wrangling the data.

The data that we obtained is not in the best condition for the analysis steps, so I need to clean some of data type in all data frame that'll be use.

```{r packages, warning=FALSE, include=FALSE}
#load the packages
library(tidyverse)
library(skimr)
library(ggpubr)
```


```{r import and cleaning all df}
#activity df
activity <- read.csv("~/Case Study/Fitabase Data 4.12.16-5.12.16/Fitbase Data Raw/dailyActivity_merged.csv") %>% 
  rename_all(tolower) %>% 
  mutate(id = as.character(id),
         activitydate = mdy(activitydate))
skim_without_charts(activity)
#caloriesHour df
caloriesHour <- read.csv("~/Case Study/Fitabase Data 4.12.16-5.12.16/Fitbase Data Raw/hourlyCalories_merged.csv") %>% 
  rename_all(tolower) %>% 
  mutate(id = as.character(id),
         activityhour = mdy_hms(activityhour))
skim_without_charts(caloriesHour)
#hourlySteps df
hourlySteps <- read.csv("~/Case Study/Fitabase Data 4.12.16-5.12.16/Fitbase Data Raw/hourlySteps_merged.csv") %>% 
  rename_all(tolower) %>% 
  mutate(id = as.character(id),
         activityhour = mdy_hms(activityhour))
skim_without_charts(hourlySteps)
#sleepday df
sleepday <- read.csv("~/Case Study/Fitabase Data 4.12.16-5.12.16/Fitbase Data Raw/sleepDay_merged.csv") %>%
  rename_all(tolower) %>% 
  mutate(id = as.character(id),
         sleepday = mdy_hms(sleepday))
skim_without_charts(sleepday)
#weighLogInfo df
weightLogInfo <- read.csv("~/Case Study/Fitabase Data 4.12.16-5.12.16/Fitbase Data Raw/weightLogInfo_merged.csv") %>% 
  rename_all(tolower) %>% 
  mutate(id = as.character(id),
         date = mdy_hms(date))
skim_without_charts(weightLogInfo)
```

From the summarized of all data that we'll analyzed, some point that need to highlight:

- Average of `totalsteps` all user is 7637, which means the average our user distance is 5 km.
- `lightactivedistance` average (3.34 km) is much more that `veryactivedistance` (1.50). Which means that we can narrowing down, that our customers activity is not that vigorously active but moderatly active.
- All data is already in good condition (no missing values, no N/A, no duplicate, no whitespace, and all the data in correct type) and ready to move for next steps (which is analysis and visualizing it).
- The difference of minutes between the most active group and the sedentary group is quite astronomic. Which is `21.2 minutes` and `991 minutes` (which is 16 hours) per days. We can encourage sedentary group to get more active to burn more calories and for their productivity.
- The Average Total of `timeinbed`(where the user decided to go to sleep) and `minutesasleep` (where the user already in REM stages) are `419 minutes` to `459 minutes` which means the averages of times our user need to get sleep soundly is `40 minutes`. We can recommend them to get active before they want to sleep our give them the notification to not playing with their gadgets before the get to sleep.
- The averages of heart rate of Bellabeat's user is `77.3 beats per min` which is can be categorizing as normal, as the normal rates is between 60-100 heart beats persecond.

*disclaimer: Since this summaries is merely on the base process. `mean` and `standard deviation` of this data may not be precise and correct, because we didn't included filter like not counting 0 values, grouping the variables, merged other necessary variable, or arrange the values.*

# Analyzing and visualizing data frames
## find some pattern of behavior

```{r analyzed and visualizing df}
#finding fav time for exercise
caloriesHour  %>% 
  ggplot(aes(hour(activityhour), calories))+
  geom_smooth(show.legend = F) +
  labs(x = "",
       y = "Calories",
       title = "User intensity while using the device by hours")
```

The graph above is telling us that the most productive time each day when the user user our product is start on 10:00 and the peak is 20:00. This means our user is the type that work in the large enviroment and can move quite frequent for the rest of their work day. We can minimalize our target market of what kind of people that like to used our product.

```{r calories that user burn everyday}
#visualizing activity df
activity %>% 
  select(activitydate, calories, id) %>% 
  group_by(id) %>% 
  ggplot(aes(activitydate, calories, fill = id)) +
  geom_boxplot(size = 0.5, show.legend = F) +
  labs(x = "",
       y = "Calories",
       title = "Calories That the User Burn Everyday")
```

```{r daily user steps}
#daily user steps
hourlySteps %>% 
  ggplot(aes(hour(activityhour), steptotal)) + 
  geom_smooth(show.legend = F) +
  labs(x = "",
       y = "Daily User Steps")
```

Just like the most productive time, this graphs give the more precise on what time our user walk the most, and our hypotesis is rigth! Most of our user walk daily in their work times.

```{r total step and how much calories they burn}
activity %>% 
  filter(totalsteps != 0) %>% 
  ggplot(aes(calories, totalsteps)) +
  geom_point() +
  geom_smooth() +
  labs(x = "Calories",
       y = "Total Steps",
       title = "Total steps of user and how much calories they burn")
```

This is quite obvious because the more they walk the more calories they burn.

```{r sleep time vs time in bed}
# create lolipop graph of two valiables so it's easy to compare them
```

```{r average activity distance}
activity %>% 
  select(veryactivedistance, moderatelyactivedistance, lightactivedistance, sedentaryactivedistance) %>%
  summarise_all(.fun = mean)
```

```{r corellation between quality of sleep and their activity movement, results = "hide"}
#created the merged df
active <- activity %>%
  inner_join(sleepday, by = c("id", "activitydate" = "sleepday")) %>% 
  select(id, activitydate, veryactivedistance, totalminutesasleep) %>% 
  ggplot(aes(x = totalminutesasleep, y = veryactivedistance)) +
  geom_point() + geom_smooth()
  labs(x = "Total mintues asleep",
       y = "Active intensity in distance")
sedentary <- activity %>% 
  inner_join(sleepday, by = c("id", "activitydate" = "sleepday")) %>% 
  select(id, activitydate, sedentaryactivedistance, totalminutesasleep) %>% 
  ggplot(aes(totalminutesasleep, sedentaryactivedistance)) +
  geom_point() + geom_smooth()
  labs(x = "Total mintues asleep",
       y = "Sedentary intensity in distance")

```

```{r combine two graph into one}
# combine two graph into one
ggarrange(active, sedentary, nrow = 1)
```

This two merge graph is my way to find some correlation of their sleep quality, between the active group and sedentary group. But turn up, there's no correlation whatsoever in there. So, we can conclude that either they have hectic activity or not. Our user sleep quality is still the same.

```{r corelattion between sleep quality and calories burn}
activity %>% 
  inner_join(sleepday, by = c("id", "activitydate" = "sleepday")) %>% 
  select(id, activitydate, calories, totalminutesasleep) %>% 
  ggplot(aes(totalminutesasleep, calories)) +
  geom_point() + geom_smooth() +
  labs(x = "Total minutes asleep",
       y = "calories",
       title = "Correlation between calories burn and sleeping quality")
```


# Conclusion

1. Main consumer that used Bellabeat product is; women how's active in their daily life and workplace, have light activity, and their average distance of their daily steps is 5 km. (*We can used this to generated more prospect consumers in the future. Because we know our main target audience*)
2. The most active times our user is between 8:00 in the morning and their peaks in 20:00 night.
3. There's no correlation between `veryactivedistance` group and `sedentaryactivedistance` group. That's mean the intensity of activity don't correlated with quality sleep. Meanwhile `moderatlyactivedistance` have more quality sleeps than `veryactivedistance` group.